---
title: "News personaliziation mock social media experiment"
author: "Bence Bago"
date: "2024-06-25"
output: pdf_document
---

```{r package, include=FALSE}
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(httr)
library(readxl)


```


```{r management}
column_names <- names(read.csv("personalization_social_media_June 28, 2024_05.24.csv", nrows = 1))

df <- read.csv("personalization_social_media_June 28, 2024_05.24.csv", sep=",", header = FALSE, skip=134)

names(df) <- column_names

df <- df %>%
  mutate(across(starts_with("bookmarked"), ~ ifelse(is.na(.) | . == '', 'false', .)))%>%
  mutate(upvote_regret=ifelse(upvote_regret==1,1,0))

duplicates <- df[duplicated(df$prolific), ]
##there is one p duplicate that produced no data twice. excluding it
df <- df[!duplicated(df$prolific), ]


ratings_columns <- grep("^vote[0-9]+$", colnames(df), value = TRUE)
statement_columns <- grep("^title[0-9]+$", colnames(df), value = TRUE)

ratings_columns <- sort(ratings_columns)
statement_columns <- sort(statement_columns)

df_long_votes <- df %>%
  select(prolific, all_of(ratings_columns)) %>%
  pivot_longer(
    cols = all_of(ratings_columns),
    names_to = "number",
    values_to = "vote",
    names_pattern = "vote([0-9]+)"
  )

df_long_titles <- df %>%
  select(prolific, all_of(statement_columns)) %>%
  pivot_longer(
    cols = all_of(statement_columns),
    names_to = "number",
    values_to = "title",
    names_pattern = "title([0-9]+)"
  )

df_long_vote <- df_long_votes %>%
  left_join(df_long_titles, by = c("prolific", "number"))

bookmark_columns <- grep("^bookmarked[0-9]+$", colnames(df), value = TRUE)
bookmarked_title_columns <- grep("^bookmarkedtitle[0-9]+$", colnames(df), value = TRUE)

bookmark_columns <- sort(bookmark_columns)
bookmarked_title_columns <- sort(bookmarked_title_columns)

df_long_bookmark <- df %>%
  select(prolific, all_of(bookmark_columns)) %>%
  pivot_longer(
    cols = all_of(bookmark_columns),
    names_to = "bookmarkorder",
    values_to = "bookmarked",
    names_pattern = "bookmarked([0-9]+)"
  )

df_long_bookmarked_titles <- df %>%
  select(prolific, all_of(bookmarked_title_columns)) %>%
  pivot_longer(
    cols = all_of(bookmarked_title_columns),
    names_to = "bookmarkorder",
    values_to = "bookmarkedtitle",
    names_pattern = "bookmarkedtitle([0-9]+)"
  )

df_long_bookmarked <- df_long_bookmark %>%
  left_join(df_long_bookmarked_titles, by = c("prolific", "bookmarkorder"))

final_df <- df_long_vote %>%
  left_join(df_long_bookmarked, by = c("prolific", "title" = "bookmarkedtitle"))



url <- "https://raw.githubusercontent.com/bencebago/news_personalization/main/filtered_data_experiment.json"
json_data <- fromJSON(url)
json_titles <-  c(json_data$title, json_data$selected_title_AbsoluteDenier)


# Assuming final_df is already created as per previous steps
# Create a new variable 'type' in final_df
final_df <- final_df %>%
  mutate(type = ifelse(title %in% json_titles, 'climate', 'neutral'))

##from original json I i should add the index for each each title for item nr that will be used for joining with the different datasets. 


####some analysis will be run on original dataset, like posterior analysis


## add columns to original dataset, most importantly climate change denier classification and statistics. 
df = df%>%
  mutate(climate_figure = ifelse(climate2==1, "Believer", ifelse(climate2==2|climate2==3, 'Denier', NA)),
         climate_stat = ifelse(climate2==1, 0.5, ifelse(climate2==2|climate2==3, -0.5, 0)),
         condition_stat = ifelse(condition=='original', 0.5, -0.5))

####
additional_columns <- c("condition", "climate1", "climate2", "prior_cause_1", "prior_happen_1", "prior_risk_1",
                        "P2..Attention.Check1", "Q6..Ideology_econ", "Q7..Ideology_social", "DemRep_C",
                        "Interest_1", "Interest_2", "Interest_3", "Interest_4", "Interest_5", "Interest_6", "Interest_7",
                        "Educational.Level", "bookmark_regret_1", "upvote_regret", "credibility_1", "selectedValue",
                        "posterior_cause_1", "posterior_happen_1", "posterior_risk_1", 'Q110', 'Q111', 'condition_stat', 'climate_stat', 'climate_figure', 'condition_stat')

additional_columns <- additional_columns[additional_columns %in% colnames(df)]

final_df <- final_df %>%
  left_join(df %>% select(prolific, all_of(additional_columns)), by = "prolific")%>%
  mutate(vote=ifelse(vote=='upvote',1,0),
         bookmarked=ifelse(bookmarked=="true",1,0))


rm(list = setdiff(ls(), c("df", "final_df")))

```

final_df is longformat data for analysing bookmarks and votes, df is the wide format data for analyzing priors, regret, credibility, posteriors

climate2 is a measure of climate change belief: Assuming global warming is happening, do you think it is… ? with 5 options: 1: Caused mostly by human activities, 2: Caused mostly by natural changes in the environment, 3, None of the above becouse global warming is not happening, 4: Other, 5: Don't know.

the question was preceded by climate1 : Recently, you may have noticed that global warming has been getting some attention in the news. Global warming refers to the idea that the world’s average temperature has been increasing over the past 150 years, may be increasing more in the future, and that the world’s climate may change as a result. What do you think: Do you think that global warming is happening? With three options: 1: Yes, 2: No, 3: Don't know.

THen we have continuous prior belief measures of 3 type: happening, cause, risk where higher value means more belief in climate change.Same for posteriors

bookmark - vote: 1:Upvoted/bookmarked 0:downvoted/not bookmarked

```{r graphs, echo=FALSE}
aggregated_data <- final_df %>%
  filter(type=='climate' & !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(vote),
    se_climate_figure = sd(vote) / sqrt(n())
  )

# Create the bar graph with error bars
ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="", 
       x='Climate belief', 
       y="Upvote (%)") +
  theme_minimal()


aggregated_data <- final_df %>%
  filter(type=='climate' & !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(bookmarked),
    se_climate_figure = sd(bookmarked) / sqrt(n())
  )

ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bookmark", 
       x="Climate belief", 
       y="Bookmarked (%)") +
  theme_minimal()

aggregated_data <- df %>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(credibility_1,na.rm=T),
    se_climate_figure = sd(credibility_1,na.rm=T) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bar Graph with Error Bars", 
       x="Climate Belief", 
       y="Credibility") +
  theme_minimal()

aggregated_data <- df %>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(bookmark_regret_1),
    se_climate_figure = sd(bookmark_regret_1) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bookmark-regret", 
       x="Climate belief", 
       y="Bookmark regret (LESS regret is higher number the scale is reversed)") +
  theme_minimal()


aggregated_data <- df %>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(upvote_regret),
    se_climate_figure = sd(upvote_regret) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Vote-regret", 
       x="Climate belief", 
       y="New upvote (%)") +
  theme_minimal()



ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  facet_wrap(~climate2) +
  labs(title="Bar Graph with Error Bars", 
       x="Belief", 
       y="Happen") +
  theme_minimal()



p <- ggplot(final_df, aes(x=prior_cause_1, y=posterior_cause_1)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color="blue") +  # Add the abline (regression line)
  geom_abline(slope=1, intercept=0, color="red", linetype="dashed") +  # Add the line of perfect correlation
  labs(title="Scatter Plot with Regression Line and Perfect Correlation Line",
       x="Prior Cause",
       y="Posterior Cause") +
  theme_minimal()
print(p)

p <- ggplot(final_df, aes(x=prior_happen_1, y=posterior_happen_1)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, color="blue") +  # Add the abline (regression line)
  geom_abline(slope=1, intercept=0, color="red", linetype="dashed") + 
    facet_wrap(~condition) +
  labs(title="Scatter Plot with Regression Line and Perfect Correlation Line",
       x="Prior Happen",
       y="Posterior Happen") +
  theme_minimal()

print(p)




```


```{r preregistered analysis, echo=FALSE}

#is there belief updating?
t.test(df[df$condition=='original',]$prior_cause_1, df[df$condition=='original',]$posterior_cause_1, paired=TRUE)
t.test(df[df$condition=='personal',]$prior_cause_1, df[df$condition=='personal',]$posterior_cause_1, paired=TRUE)

t.test(df[df$condition=='original',]$prior_happen_1, df[df$condition=='original',]$posterior_happen_1, paired=TRUE)
t.test(df[df$condition=='personal',]$prior_happen_1, df[df$condition=='personal',]$posterior_happen_1, paired=TRUE)

t.test(df[df$condition=='original',]$prior_risk_1, df[df$condition=='original',]$posterior_risk_1, paired=TRUE)
t.test(df[df$condition=='personal',]$prior_risk_1, df[df$condition=='personal',]$posterior_risk_1, paired=TRUE)


##condition has an effect on posteriors?
model1=lmer(posterior_happen_1 ~ condition+ (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(posterior_cause_1 ~ condition + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(posterior_risk_1 ~ condition + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


#preregistered analysis
model1=lmer(credibility_1 ~ condition_stat*climate_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(bookmark_regret_1 ~ condition_stat*climate_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(upvote_regret ~ condition_stat*climate_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


model1=lmer(bookmarked ~ condition_stat*climate_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat*climate_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)


#Continuous measures
model1=lmer(bookmarked ~ condition_stat*prior_happen_1 + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat*prior_cause_1 + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)


model1=lmer(vote ~ condition_stat*prior_happen_1 + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat*prior_cause_1 + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)


##bookmark regret effect is not significant with prior_happen, the rest replicates the dichotomous analysis
model1=lmer(credibility_1 ~ condition_stat*prior_happen_1  + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(bookmark_regret_1 ~ condition_stat*prior_happen_1  + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(upvote_regret ~ condition_stat*prior_happen_1  + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)



model1=lmer(credibility_1 ~ condition_stat*prior_cause_1 + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(bookmark_regret_1 ~ condition_stat*prior_cause_1 + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(upvote_regret ~ condition_stat*prior_cause_1 + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)




```


```{r item level heterogeneity}
#create item_level-bookmark and item level bookmarking situations.
# URL of the JSON file on GitHub
json_url <- "https://raw.githubusercontent.com/bencebago/news_personalization/main/filtered_relevant_articles_science.json"

json_data <- fromJSON(content(GET(json_url), "text", encoding = "UTF-8"))

# Read the response_factcheck.xlsx file
response_factcheck <- read_excel("response_factcheck.xlsx")

# Define the find_row function
find_row <- function(statement, df) {
  for (i in seq_len(nrow(df))) {
    if (statement %in% df[i, ]) {
      return(i)
    }
  }
  return(NA)
}

# Add item_nr to df
df <- df %>%
  mutate(item_nr = map_int(selectedValue, ~ find_row(.x, json_data)))

# Add item_nr to final_df
final_df <- final_df %>%
  mutate(item_nr = map_int(title, ~ find_row(.x, json_data)))


response_factcheck <-response_factcheck %>%
   mutate(item_nr = map_int(title, ~ find_row(.x, json_data)))


response_relevance <- response_factcheck %>%
  select(item_nr, relevance)

# Merge relevance column with df based on item_nr
df <- df %>%
  left_join(response_relevance, by = "item_nr")%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))

# Merge relevance column with final_df based on item_nr
final_df <- final_df %>%
  left_join(response_relevance, by = "item_nr")%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))




##now calculate average vote and bookmark value for each item
average_df <- final_df %>%
  group_by(item_nr, condition,climate2) %>%
  summarise(
    average_vote = mean(vote, na.rm = TRUE),
    average_bookmark = mean(bookmarked, na.rm = TRUE)
  ) %>%
  ungroup()

# Pivot the data to wide format to separate the conditions
average_wide_df <- average_df %>%
  pivot_wider(
    names_from = condition,
    values_from = c(average_vote, average_bookmark),
    names_prefix = "condition_"
  )

# Calculate the differences between the conditions
average_diff_df <- average_wide_df %>%
  mutate(
    original_vote_average = average_vote_condition_original,
    personal_vote_average = average_vote_condition_personal,
    original_bookmark_average = average_bookmark_condition_original,
    personal_bookmark_average = average_bookmark_condition_personal,
    vote_difference = original_vote_average - personal_vote_average,
    bookmark_difference = original_bookmark_average - personal_bookmark_average
  )

# Select and rename the desired columns
average_final_df <- average_diff_df %>%
  select(
    item_nr,
    original_vote_average,
    personal_vote_average,
    vote_difference,
    original_bookmark_average,
    personal_bookmark_average,
    bookmark_difference,
    climate2
  )

###save diff dataset and add it based on item nrs
diff_data = read.csv('diff_data.csv', header=T)

average_final_df <- average_final_df%>%
  left_join(diff_data, by = 'item_nr')%>%
  left_join(response_relevance, by = "item_nr")%>%
  filter(climate2==2|climate2==3)%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))



cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_agreement_distance)
cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_regret_distance)
cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_positive_distance)
cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_negative_distance)


cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_agreement_distance)
cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_regret_distance)
cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_positive_distance)
cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_negative_distance)


cor.test(average_final_df$vote_difference, average_final_df$relevance)
cor.test(average_final_df$bookmark_difference, average_final_df$relevance)



##now df regret measures


average_df <- df %>%
  group_by(item_nr, condition,climate2) %>%
  summarise(
    average_vote_regret = mean(upvote_regret, na.rm = TRUE),
    average_bookmark_regret = mean(bookmark_regret_1, na.rm = TRUE)
  ) %>%
  ungroup()

# Pivot the data to wide format to separate the conditions
average_wide_df <- average_df %>%
  pivot_wider(
    names_from = condition,
    values_from = c(average_vote_regret, average_bookmark_regret),
    names_prefix = "condition_"
  )

# Calculate the differences between the conditions
average_diff_df <- average_wide_df %>%
  mutate(
    original_vote_regret_average = average_vote_regret_condition_original,
    personal_vote_regret_average = average_vote_regret_condition_personal,
    original_bookmark_regret_average = average_bookmark_regret_condition_original,
    personal_bookmark_regret_average = average_bookmark_regret_condition_personal,
    vote_difference = original_vote_regret_average - personal_vote_regret_average,
    bookmark_difference = original_bookmark_regret_average - personal_bookmark_regret_average
  )

# Select and rename the desired columns
average_final_df <- average_diff_df %>%
  select(
    item_nr,
    original_vote_regret_average,
    personal_vote_regret_average,
    vote_difference,
    original_bookmark_regret_average,
    personal_bookmark_regret_average,
    bookmark_difference,
    climate2
  )

average_final_df <- average_final_df%>%
  left_join(diff_data, by = 'item_nr')%>%
  left_join(response_relevance, by = "item_nr")%>%
  filter(climate2==2|climate2==3)%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))

cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_agreement_distance)
cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_regret_distance)
cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_positive_distance)
cor.test(average_final_df$vote_difference, average_final_df$AbsoluteDenier_negative_distance)


cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_agreement_distance)
cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_regret_distance)
cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_positive_distance)
cor.test(average_final_df$bookmark_difference, average_final_df$AbsoluteDenier_negative_distance)

####nothing to see here on the regret side of things.



###heterogeneity on relevance
cor.test(average_final_df$vote_difference, average_final_df$relevance)
cor.test(average_final_df$bookmark_difference, average_final_df$relevance)



```

```{r new regret analysis}

cor.test(final_df[final_df$condition=='personal',]$relevance, final_df[final_df$condition=='personal',]$vote)
cor.test(final_df[final_df$condition=='personal',]$relevance, final_df[final_df$condition=='personal',]$bookmarked)


cor.test(df[df$condition=='personal',]$relevance, df[df$condition=='personal',]$upvote_regret)
cor.test(df[df$condition=='personal',]$relevance, df[df$condition=='personal',]$bookmark_regret_1)


cor.test(final_df[final_df$condition=='personal' & (final_df$climate2==2|final_df$climate2==3|final_df$climate2==4),]$relevance, final_df[final_df$condition=='personal' & (final_df$climate2==2|final_df$climate2==3|final_df$climate2==4),]$vote)
cor.test(final_df[final_df$condition=='personal' & (final_df$climate2==2|final_df$climate2==3|final_df$climate2==4),]$relevance, final_df[final_df$condition=='personal' & (final_df$climate2==2|final_df$climate2==3|final_df$climate2==4),]$bookmarked)


cor.test(df[df$condition=='personal' & (df$climate2==2|df$climate2==3|df$climate2==4),]$relevance, df[df$condition=='personal'& (df$climate2==2|df$climate2==3|df$climate2==4),]$upvote_regret)
cor.test(df[df$condition=='personal'& (df$climate2==2|df$climate2==3|df$climate2==4),]$relevance, df[df$condition=='personal'& (df$climate2==2|df$climate2==3|df$climate2==4),]$bookmark_regret_1)
##no correlation between regret, or engagement and relevance


#####analyse regret, did the article meet expectations?
df2 <- df %>%
  left_join(final_df %>% select(title, vote, prolific), 
            by = c("selectedValue" = "title", "prolific" = "prolific"))%>%
  mutate(voteregret = ifelse(vote==1 & upvote_regret==1, '11', ifelse(vote==1 & upvote_regret==0, '10', ifelse(vote==0 & upvote_regret==1, '01', '00'))))

cor.test(df2[df2$condition=='personal' & (df2$climate2==2|df2$climate2==3|df2$climate2==4),]$vote, df2[df2$condition=='personal'& (df2$climate2==2|df2$climate2==3|df2$climate2==4),]$upvote_regret)



df2_clean <- df2 %>%
  filter(!is.na(voteregret), !is.na(condition), !is.na(climate2))%>%
  mutate(denier = ifelse(climate2==1, 'Believer', ifelse(climate2==4, NA, 'Denier')),
  change = ifelse(voteregret == '01' | voteregret== '10', 'Vote regretted', 'Vote NOT regretted'),
  statchange =ifelse(change=='Vote regretted', 1,0),
  believerstat = ifelse(denier=='Denier', -0.5,0.5),
  conditionstat = ifelse(condition == 'original',0,1),
  bookmark_regret = 100-bookmark_regret_1)

# Create a contingency table
table(df2_clean$condition, df2_clean$change, df2_clean$denier)
table(df2_clean[df2_clean$denier == 'Denier',]$condition, df2_clean[df2_clean$denier == 'Denier',]$change)


model1 = lm(statchange ~ believerstat*conditionstat, data=df2_clean, na.action = na.omit)
summary(model1)
model1 = lm(statchange ~ conditionstat, data=df2_clean[df2_clean$denier=='Believer',], na.action = na.omit)
summary(model1)

model1 = lm(statchange ~ conditionstat, data=df2_clean[df2_clean$denier=='Denier',], na.action = na.omit)
summary(model1)


######testing for self-selection (people self-select into different articles in the two different conditions) there is moderate effect here
prob_df <- df2_clean %>%
  group_by(denier, condition, item_nr) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(denier, condition) %>%
  mutate(probability = count / sum(count)) %>%
  select(denier, condition, item_nr, probability) %>%
  pivot_wider(names_from = condition, values_from = probability, values_fill = 0) %>%
  rename(prob_original = `original`, prob_personal = `personal`)

# Calculate the correlation for each denier
correlation_results <- prob_df %>%
  group_by(denier) %>%
  summarise(correlation = cor(prob_original, prob_personal, use = "complete.obs"))

print(correlation_results)


####do this on final_df bookmarked

prob_final_df <- final_df %>%
  filter(!is.na(bookmarked), !is.na(condition), !is.na(climate2))%>%
  mutate(denier = ifelse(climate2==1, 'Believer', ifelse(climate2==4, NA, 'Denier')))%>%
  group_by(denier, condition, item_nr) %>%
  summarise(count = n(), bookmarked_sum = sum(bookmarked, na.rm = TRUE), .groups = 'drop') %>%
  group_by(denier, condition) %>%
  mutate(probability = bookmarked_sum / count) %>%
  select(denier, condition, item_nr, probability) %>%
  pivot_wider(names_from = condition, values_from = probability, values_fill = 0) %>%
  rename(prob_original = `original`, prob_personal = `personal`)


correlation_results <- prob_final_df %>%
  group_by(denier) %>%
  summarise(correlation = cor(prob_original, prob_personal, use = "complete.obs"))

print(correlation_results)


####do this on voted
prob_final_df <- final_df %>%
  filter(!is.na(vote), !is.na(condition), !is.na(climate2))%>%
  mutate(denier = ifelse(climate2==1, 'Believer', ifelse(climate2==4, NA, 'Denier')))%>%
  group_by(denier, condition, item_nr) %>%
  summarise(count = n(), voted_sum = sum(vote, na.rm = TRUE), .groups = 'drop') %>%
  group_by(denier, condition) %>%
  mutate(probability = voted_sum / count) %>%
  select(denier, condition, item_nr, probability) %>%
  pivot_wider(names_from = condition, values_from = probability, values_fill = 0) %>%
  rename(prob_original = `original`, prob_personal = `personal`)


correlation_results <- prob_final_df %>%
  group_by(denier) %>%
  summarise(correlation = cor(prob_original, prob_personal, use = "complete.obs"))

print(correlation_results)


###analyse bookmark regrets, but only on headlines people upvoted and bookmarked so really wanted to see

##do the two stats on upvoted and bookmarked headlines
aggregated_data <- df2_clean %>%
    filter(vote==1)%>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(bookmark_regret),
    se_climate_figure = sd(bookmark_regret) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bookmark-regret", 
       x="Climate belief", 
       y="Bookmark regret") +
  theme_minimal()


```