---
title: "News personaliziation mock social media experiment"
author: "Bence Bago"
date: "2024-06-25"
output: pdf_document
---

```{r package, include=FALSE}
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(httr)
library(readxl)
library(broom)
library(purrr)
library(dplyr)
library(tidytext)
library(textdata)
library(moments)

```


```{r management}
column_names <- names(read.csv("personalization_social_media_June 28, 2024_05.24.csv", nrows = 1))

df <- read.csv("personalization_social_media_June 28, 2024_05.24.csv", sep=",", header = FALSE, skip=134)

names(df) <- column_names

df <- df %>%
  mutate(across(starts_with("bookmarked"), ~ ifelse(is.na(.) | . == '', 'false', .)))%>%
  mutate(upvote_regret=ifelse(upvote_regret==1,1,0))

duplicates <- df[duplicated(df$prolific), ]
##there is one p duplicate that produced no data twice. excluding it
df <- df[!duplicated(df$prolific), ]


ratings_columns <- grep("^vote[0-9]+$", colnames(df), value = TRUE)
statement_columns <- grep("^title[0-9]+$", colnames(df), value = TRUE)

ratings_columns <- sort(ratings_columns)
statement_columns <- sort(statement_columns)

df_long_votes <- df %>%
  select(prolific, all_of(ratings_columns)) %>%
  pivot_longer(
    cols = all_of(ratings_columns),
    names_to = "number",
    values_to = "vote",
    names_pattern = "vote([0-9]+)"
  )

df_long_titles <- df %>%
  select(prolific, all_of(statement_columns)) %>%
  pivot_longer(
    cols = all_of(statement_columns),
    names_to = "number",
    values_to = "title",
    names_pattern = "title([0-9]+)"
  )

df_long_vote <- df_long_votes %>%
  left_join(df_long_titles, by = c("prolific", "number"))

bookmark_columns <- grep("^bookmarked[0-9]+$", colnames(df), value = TRUE)
bookmarked_title_columns <- grep("^bookmarkedtitle[0-9]+$", colnames(df), value = TRUE)

bookmark_columns <- sort(bookmark_columns)
bookmarked_title_columns <- sort(bookmarked_title_columns)

df_long_bookmark <- df %>%
  select(prolific, all_of(bookmark_columns)) %>%
  pivot_longer(
    cols = all_of(bookmark_columns),
    names_to = "bookmarkorder",
    values_to = "bookmarked",
    names_pattern = "bookmarked([0-9]+)"
  )

df_long_bookmarked_titles <- df %>%
  select(prolific, all_of(bookmarked_title_columns)) %>%
  pivot_longer(
    cols = all_of(bookmarked_title_columns),
    names_to = "bookmarkorder",
    values_to = "bookmarkedtitle",
    names_pattern = "bookmarkedtitle([0-9]+)"
  )

df_long_bookmarked <- df_long_bookmark %>%
  left_join(df_long_bookmarked_titles, by = c("prolific", "bookmarkorder"))

final_df <- df_long_vote %>%
  left_join(df_long_bookmarked, by = c("prolific", "title" = "bookmarkedtitle"))



url <- "https://raw.githubusercontent.com/bencebago/news_personalization/main/filtered_data_experiment.json"
json_data <- fromJSON(url)
json_titles <-  c(json_data$title, json_data$selected_title_AbsoluteDenier)


# Assuming final_df is already created as per previous steps
# Create a new variable 'type' in final_df
final_df <- final_df %>%
  mutate(type = ifelse(title %in% json_titles, 'climate', 'neutral'))

##from original json I i should add the index for each each title for item nr that will be used for joining with the different datasets. 


####some analysis will be run on original dataset, like posterior analysis


## add columns to original dataset, most importantly climate change denier classification and statistics. 
df = df%>%
  mutate(climate_figure = ifelse(climate2==1, "Believer", ifelse(climate2==2|climate2==3|climate2==5, 'Denier', NA)),
         climate_stat = ifelse(climate2==1, 1, ifelse(climate2==2|climate2==3, -1, 0)),
         condition_stat = ifelse(condition=='original', 0, 1),
         cause_change = prior_cause_1 - posterior_cause_1,
         risk_change = prior_risk_1 - posterior_risk_1,
         happen_change = prior_happen_1 - posterior_happen_1,
         posterior_happen_1 = posterior_happen_1 -50,
         posterior_risk_1 = posterior_risk_1-50,
         posterior_cause_1 = posterior_cause_1-50,
         prior_cause_1 = prior_cause_1-50,
         prior_happen_1 = prior_happen_1-50,
         prior_risk_1 = prior_risk_1-50)

####
additional_columns <- c("condition", "climate1", "climate2", "prior_cause_1", "prior_happen_1", "prior_risk_1",
                        "P2..Attention.Check1", "Q6..Ideology_econ", "Q7..Ideology_social", "DemRep_C",
                        "Interest_1", "Interest_2", "Interest_3", "Interest_4", "Interest_5", "Interest_6", "Interest_7",
                        "Educational.Level", "bookmark_regret_1", "upvote_regret", "credibility_1", "selectedValue",
                        "posterior_cause_1", "posterior_happen_1", "posterior_risk_1", 'Q110', 'Q111', 'Q133', 'Q134', 'condition_stat', 'climate_stat', 'climate_figure', 'condition_stat')

additional_columns <- additional_columns[additional_columns %in% colnames(df)]

final_df <- final_df %>%
  left_join(df %>% select(prolific, all_of(additional_columns)), by = "prolific")%>%
  mutate(vote=ifelse(vote=='upvote',1,0),
         bookmarked=ifelse(bookmarked=="true",1,0))
  
         
         


rm(list = setdiff(ls(), c("df", "final_df")))

```

final_df is longformat data for analysing bookmarks and votes, df is the wide format data for analyzing priors, regret, credibility, posteriors

climate2 is a measure of climate change belief: Assuming global warming is happening, do you think it is… ? with 5 options: 1: Caused mostly by human activities, 2: Caused mostly by natural changes in the environment, 3, None of the above becouse global warming is not happening, 4: Other, 5: Don't know.

the question was preceded by climate1 : Recently, you may have noticed that global warming has been getting some attention in the news. Global warming refers to the idea that the world’s average temperature has been increasing over the past 150 years, may be increasing more in the future, and that the world’s climate may change as a result. What do you think: Do you think that global warming is happening? With three options: 1: Yes, 2: No, 3: Don't know.

THen we have continuous prior belief measures of 3 type: happening, cause, risk where higher value means more belief in climate change.Same for posteriors

bookmark - vote: 1:Upvoted/bookmarked 0:downvoted/not bookmarked

```{r graphs, echo=FALSE}
aggregated_data <- final_df %>%
  filter(type=='climate' & !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(vote),
    se_climate_figure = sd(vote) / sqrt(n())
  )

# Create the bar graph with error bars
ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="", 
       x='Climate belief', 
       y="Upvote (%)") +
  theme_minimal()


aggregated_data <- final_df %>%
  filter(type=='climate' & !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(bookmarked),
    se_climate_figure = sd(bookmarked) / sqrt(n())
  )

ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bookmark", 
       x="Climate belief", 
       y="Bookmarked (%)") +
  theme_minimal()

aggregated_data <- df %>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(credibility_1,na.rm=T),
    se_climate_figure = sd(credibility_1,na.rm=T) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bar Graph with Error Bars", 
       x="Climate Belief", 
       y="Credibility") +
  theme_minimal()

aggregated_data <- df %>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(bookmark_regret_1),
    se_climate_figure = sd(bookmark_regret_1) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Bookmark-regret", 
       x="Climate belief", 
       y="Bookmark regret (LESS regret is higher number the scale is reversed)") +
  theme_minimal()


aggregated_data <- df %>%
  filter( !is.na(condition) & !is.na(climate_figure))%>%
  group_by(climate_figure, condition) %>%
  summarise(
    mean_climate_figure = mean(upvote_regret),
    se_climate_figure = sd(upvote_regret) / sqrt(n())
  )


ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  labs(title="Vote-regret", 
       x="Climate belief", 
       y="New upvote (%)") +
  theme_minimal()



ggplot(aggregated_data, aes(x=climate_figure, y=mean_climate_figure, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width=0.7) +
  geom_errorbar(aes(ymin=mean_climate_figure - se_climate_figure, ymax=mean_climate_figure + se_climate_figure), 
                width=0.2, 
                position=position_dodge(0.7)) +
  facet_wrap(~climate2) +
  labs(title="Bar Graph with Error Bars", 
       x="Belief", 
       y="Happen") +
  theme_minimal()

p <- ggplot(final_df, aes(x=prior_risk_1, y=posterior_risk_1)) +
  geom_smooth(method=lm, se=FALSE, color="blue") +  # Add the abline (regression line)
  geom_abline(slope=1, intercept=50, color="red", linetype="dashed") +  # Add the line of perfect correlation
  labs(title="Likelihood of climate change having harmful consequences for humanity",
       x="Prior Risk",
       y="Posterior Risk") +
  theme_minimal()
print(p)


p <- ggplot(final_df, aes(x=prior_cause_1, y=posterior_cause_1)) +
  geom_smooth(method=lm, se=FALSE, color="blue") +  # Add the abline (regression line)
  geom_abline(slope=1, intercept=50, color="red", linetype="dashed") +  # Add the line of perfect correlation
  labs(title="Likelihood of climate change caused by human activity",
       x="Prior Cause",
       y="Posterior Cause") +
  theme_minimal()
print(p)

p <- ggplot(final_df, aes(x=prior_happen_1, y=posterior_happen_1)) +
  geom_smooth(method=lm, se=FALSE, color="blue") +  # Add the abline (regression line)
  geom_abline(slope=1, intercept=50, color="red", linetype="dashed") + 
  labs(title="Likelihood of climate change happening",
       x="Prior Happen",
       y="Posterior Happen") +
  theme_minimal()

print(p)




```


```{r engagement analysis, echo=FALSE}
table(df$climate2)
#is there belief updating?
t.test(df[df$condition=='original',]$prior_cause_1, df[df$condition=='original',]$posterior_cause_1, paired=TRUE)
t.test(df[df$condition=='personal',]$prior_cause_1, df[df$condition=='personal',]$posterior_cause_1, paired=TRUE)

t.test(df[df$condition=='original',]$prior_happen_1, df[df$condition=='original',]$posterior_happen_1, paired=TRUE)
t.test(df[df$condition=='personal',]$prior_happen_1, df[df$condition=='personal',]$posterior_happen_1, paired=TRUE)

t.test(df[df$condition=='original',]$prior_risk_1, df[df$condition=='original',]$posterior_risk_1, paired=TRUE)
t.test(df[df$condition=='personal',]$prior_risk_1, df[df$condition=='personal',]$posterior_risk_1, paired=TRUE)

quantile(df$prior_happen_1,na.rm=T)
quantile(df$prior_cause_1, na.rm=T)
quantile(df$prior_risk_1, na.rm=T)


# Create a function to count the number of data points within the specified ranges
count_ranges <- function(x) {
  c(
    sum(x >= -50 & x <= -25, na.rm=T),
    sum(x >= -24 & x <= 0,na.rm=T),
    sum(x >= 1 & x <= 25,na.rm=T),
    sum(x >= 26 & x <= 50,na.rm=T)
  )
}

# Apply the function to each variable and create a table
result_table <- data.frame(
  Range = c("[-50, -25]", "[-24, 0]", "[1, 25]", "[26, 50]"),
  prior_happen_1 = count_ranges(df$prior_happen_1),
  prior_risk_1 = count_ranges(df$prior_risk_1),
  prior_cause_1 = count_ranges(df$prior_cause_1)
)

# Print the result table
print(result_table)

##condition has an effect on posteriors?
model1=lmer(posterior_happen_1 ~ condition+ (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(posterior_cause_1 ~ condition + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(posterior_risk_1 ~ condition + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


model1=lmer(cause_change ~ condition+ (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lm(happen_change ~ condition, data=df, na.action=na.omit)
summary(model1)

model1=lmer(risk_change ~ condition+ (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


#preregistered analysis
data= final_df[final_df$type=='climate',]

model1=lmer(bookmarked ~ condition_stat*climate_stat + (1|title)+ (1|prolific), data=data, na.action=na.omit)
summary(model1)


model1=lmer(vote ~ climate_stat*condition_stat + (1|title)+ (1|prolific), data=data, na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat + (1|title)+ (1|prolific), data=data[data$prior_happen_1 < -24,],  na.action=na.omit)
summary(model1)

#Continuous measures
model1=lmer(bookmarked ~ condition_stat*scale(prior_happen_1) + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat*scale(prior_cause_1) + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat*scale(prior_risk_1) + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)


model1=lmer(vote ~ condition_stat*scale(prior_happen_1) + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat*scale(prior_cause_1) + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat*scale(prior_risk_1) + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate',], na.action=na.omit)
summary(model1)






####most skeptical audience
model1=lmer(bookmarked ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_happen_1 < -24, ], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_cause_1 < -24,], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_risk_1 < -24,], na.action=na.omit)
summary(model1)


model1=lmer(vote ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_happen_1 < -24, ], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_cause_1 < -24,], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat+ (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_risk_1 < -24,,], na.action=na.omit)
summary(model1)

#least skeptical audience


model1=lmer(bookmarked ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_happen_1 > 24, ], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_cause_1 > 24,], na.action=na.omit)
summary(model1)

model1=lmer(bookmarked ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_risk_1 > 24,], na.action=na.omit)
summary(model1)


model1=lmer(vote ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_happen_1 > 24, ], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat + (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_cause_1 > 24,], na.action=na.omit)
summary(model1)

model1=lmer(vote ~ condition_stat+ (1|title)+ (1|prolific), data=final_df[final_df$type=='climate' & final_df$prior_risk_1 > 24,,], na.action=na.omit)
summary(model1)

cor.test(final_df$vote, final_df$bookmarked)

```



```{r backfire analysis, echo=FALSE}
#vote
df2 <- df %>%
  left_join(final_df %>% select(title, vote, prolific), 
            by = c("selectedValue" = "title", "prolific" = "prolific"))%>%
  mutate(voteregret = ifelse(vote==1 & upvote_regret==1, '11', ifelse(vote==1 & upvote_regret==0, '10', ifelse(vote==0 & upvote_regret==1, '01', '00'))))

mean(df2[df2$condition=='personal' & (df2$climate2==2|df2$climate2==3|df2$climate2==5),]$upvote_regret, na.rm=T)-
mean(df2[df2$condition=='personal' & (df2$climate2==2|df2$climate2==3|df2$climate2==5),]$vote, na.rm=T)

mean(df2[df2$condition=='original' & (df2$climate2==2|df2$climate2==3|df2$climate2==5),]$upvote_regret, na.rm=T)-
mean(df2[df2$condition=='original' & (df2$climate2==2|df2$climate2==3|df2$climate2==5),]$vote, na.rm=T)


mean(df2[df2$condition=='personal' & (df2$climate2==1),]$upvote_regret, na.rm=T)-
mean(df2[df2$condition=='personal' & (df2$climate2==1),]$vote, na.rm=T)

mean(df2[df2$condition=='original' & (df2$climate2==1),]$upvote_regret, na.rm=T)-
mean(df2[df2$condition=='original' & (df2$climate2==1),]$vote, na.rm=T)


df2_clean <- df2 %>%
  filter(!is.na(voteregret), !is.na(condition), !is.na(climate2))%>%
  mutate(denier = ifelse(climate2==1, 'Believer', ifelse(climate2==4, NA, 'Denier')),
  believerstat = ifelse(climate2==1, 1, ifelse(climate2==2|climate2==3, -1, 0)),
  change = ifelse(voteregret == '01' | voteregret== '10', 'Vote regretted', 'Vote NOT regretted'),
  statchange =ifelse(change=='Vote regretted', 1,0),
  conditionstat = ifelse(condition == 'original',0,1),
  bookmark_regret = 100-bookmark_regret_1)

# Create a contingency table
table(df2_clean$condition, df2_clean$voteregret, df2_clean$denier)
table(df2_clean[df2_clean$denier == 'Denier',]$condition, df2_clean[df2_clean$denier == 'Denier',]$change)

df2_clean_vote = df2_clean %>%
    filter(voteregret== '10'| voteregret=='11')

model1 = lmer(statchange ~ believerstat*conditionstat + (1|selectedValue), data=df2_clean_vote, na.action = na.omit)
summary(model1)

model1 = lmer(statchange ~ scale(prior_cause_1)*conditionstat + (1|selectedValue), data=df2_clean_vote, na.action = na.omit)
summary(model1)

model1 = lmer(statchange ~ scale(prior_happen_1)*conditionstat + (1|selectedValue), data=df2_clean_vote, na.action = na.omit)
summary(model1)

model1 = lmer(statchange ~ scale(prior_risk_1)*conditionstat + (1|selectedValue), data=df2_clean_vote, na.action = na.omit)
summary(model1)



#bookmark


model1=lmer(scale(bookmark_regret_1) ~ condition_stat*climate_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(scale(bookmark_regret_1) ~ condition_stat*scale(prior_happen_1)  + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


model1=lmer(scale(bookmark_regret_1) ~ condition_stat*scale(prior_cause_1) + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(scale(bookmark_regret_1) ~ condition_stat*scale(prior_risk_1) + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


#trust

model1=lmer(scale(credibility_1) ~ condition_stat*climate_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(scale(credibility_1) ~ condition_stat*scale(prior_happen_1)  + (condition_stat|selectedValue), data=df, na.action=na.omit)
summary(model1)

model1=lmer(scale(credibility_1) ~ condition_stat*scale(prior_cause_1) + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)


model1=lmer(scale(credibility_1) ~ condition_stat*scale(prior_risk_1)  + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)
```


```{r item level heterogeneity}
#create item_level-bookmark and item level bookmarking situations.
# URL of the JSON file on GitHub
json_url <- "https://raw.githubusercontent.com/bencebago/news_personalization/main/filtered_relevant_articles_science.json"

json_data <- fromJSON(content(GET(json_url), "text", encoding = "UTF-8"))

# Function to count words in a single string
count_words <- function(string) {
  words <- strsplit(string, "\\s+")
  return(length(unlist(words)))
}

# Apply the function to each string in the vector
json_data$wordcount <- sapply(json_data$text, count_words)

# Read the response_factcheck.xlsx file
response_factcheck <- read_excel("response_factcheck.xlsx")

# Define the find_row function
find_row <- function(statement, df) {
  for (i in seq_len(nrow(df))) {
    if (statement %in% df[i, ]) {
      return(i)
    }
  }
  return(NA)
}

# Add item_nr to df
df <- df %>%
  mutate(item_nr = map_int(selectedValue, ~ find_row(.x, json_data)))

df <- df %>%
  mutate(wordcount = ifelse(!is.na(item_nr), json_data$wordcount[item_nr], NA))

# Add item_nr to final_df
final_df <- final_df %>%
  mutate(item_nr = map_int(title, ~ find_row(.x, json_data)))


response_factcheck <-response_factcheck %>%
   mutate(item_nr = map_int(title, ~ find_row(.x, json_data)))


response_relevance <- response_factcheck %>%
  select(item_nr, relevance)

jsonlength=json_data %>%
  select(item_nr)

# Merge relevance column with df based on item_nr
df <- df %>%
  left_join(response_relevance, by = "item_nr")%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))

# Merge relevance column with final_df based on item_nr
final_df <- final_df %>%
  left_join(response_relevance, by = "item_nr")%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))




average_df <- final_df %>%
  group_by(item_nr, condition,climate2) %>% 
  summarise(
    average_vote = mean(vote, na.rm = TRUE),
    average_bookmark = mean(bookmarked, na.rm = TRUE)
  ) %>%
  ungroup()

average_wide_df <- average_df %>%
  pivot_wider(
    names_from = condition,
    values_from = c(average_vote, average_bookmark),
    names_prefix = "condition_"
  )

average_diff_df <- average_wide_df %>%
  mutate(
    original_vote_average = average_vote_condition_original,
    personal_vote_average = average_vote_condition_personal,
    original_bookmark_average = average_bookmark_condition_original,
    personal_bookmark_average = average_bookmark_condition_personal,
    vote_difference = original_vote_average - personal_vote_average,
    bookmark_difference = original_bookmark_average - personal_bookmark_average
  )

average_final_df <- average_diff_df %>%
  select(
    item_nr,
    original_vote_average,
    personal_vote_average,
    vote_difference,
    original_bookmark_average,
    personal_bookmark_average,
    bookmark_difference,
    climate2
  )

diff_data = read.csv('diff_data.csv', header=T)

average_final_df <- average_final_df%>%
  left_join(diff_data, by = 'item_nr')%>%
  left_join(response_relevance, by = "item_nr")%>%
  mutate(relevance = ifelse(relevance == 4, 0, 1))


rm(list = setdiff(ls(), c("df", "final_df", 'average_final_df')))

```


```{r headline linguistic analysis}
df <- read_excel('headlines_analysis_clickbait.xlsx')

df <- df %>%
  mutate(
    NegativeOriginal = as.numeric(NegativeOriginal),
    SensationalOriginal = as.numeric(SensationalOriginal),
    EmotionalOriginal = as.numeric(EmotionalOriginal),
    ConsistencyOriginal = as.numeric(ConsistencyOriginal),
    MisleadingOriginal = as.numeric(MisleadingOriginal),
    NegativeFlipped = as.numeric(NegativeFlipped),
    SensationalFlipped = as.numeric(SensationalFlipped),
    EmotionalFlipped = as.numeric(EmotionalFlipped),
    ConsistencyFlipped = as.numeric(ConsistencyFlipped),
    MisleadingFlipped = as.numeric(MisleadingFlipped)
  )

df_long <- df %>%
  pivot_longer(
    cols = starts_with("Negative") | starts_with("Sensational") | starts_with("Emotional") | starts_with("Consistency")| starts_with("Misleading"),
    names_to = c("Metric", "Type"),
    names_pattern = "(Negative|Sensational|Emotional|Consistency|Misleading)(Original|Flipped)",
    values_to = "Score"
  )

t_test_results <- df_long %>%
  pivot_wider(names_from = Type, values_from = Score, names_prefix = "Score_") %>%
  group_by(Metric) %>%
  summarize(
    t_test = list(t.test(Score_Original, Score_Flipped, paired = TRUE) %>% tidy())
  ) %>%
  unnest(t_test)
# Display results
print(t_test_results)



# Create a box-scatterplot using ggplot2
ggplot(df_long, aes(x = Type, y = Score, color = Type)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(width = 0.2, alpha = 0.7) +
  facet_wrap(~ Metric, scales = "free_y") + # Facet by the metric
  labs(
    title = "Comparison of Original and Flipped Headlines",
    x = "Type",
    y = "Score"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


```


```{r posterior analysis, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

ttest1=t.test(df$happen_change)
ttest2=t.test(df$cause_change)
ttest3=t.test(df$risk_change)

df$prior=df$prior_happen_1
model1=lmer(happen_change~ I(prior^2) + prior + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

df$prior=df$prior_cause_1
model2=lmer(cause_change~ I(prior^2) + prior + (1|selectedValue), data=df, na.action=na.omit)
summary(model2)

model3=lmer(risk_change~ I(prior^2) +prior + (1|selectedValue), data=df, na.action=na.omit)
summary(model3)

df$prior=df$prior_happen_1
model1=lmer(happen_change ~ condition_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

df$prior=df$prior_cause_1
model2=lmer(cause_change ~ condition_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model2)

df$prior=df$prior_risk_1
model3=lmer(risk_change ~ condition_stat + (1|selectedValue), data=df, na.action=na.omit)
summary(model3)

df$prior=df$prior_happen_1
model1=lmer(happen_change ~ Partisanship + (1|selectedValue), data=df, na.action=na.omit)
summary(model1)

df$prior=df$prior_cause_1
model2=lmer(cause_change ~ Partisanship + (1|selectedValue), data=df, na.action=na.omit)
summary(model2)

df$prior=df$prior_risk_1
model3=lmer(risk_change ~ Partisanship + (1|selectedValue), data=df, na.action=na.omit)
summary(model3)

t.test(df[df$partisan_identity=='Republican',]$risk_change)
t.test(df[df$partisan_identity=='Democrat',]$risk_change)

```


